---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statsummary

<!-- badges: start -->
<!-- badges: end -->

The goal of statsummary is to compute summary statistics (mean, median, minimum, maximum, count) on a numeric variable grouped by a categorical variable.

## Installation

statsummary is not yet on CRAN. You can install the development version of statsummary like so:

``` r
devtools::install_github("eamutaigwe/statsummary")
```

## Example

Summarize_data() is a function that helps to carry out a fairly common task on a dataset which quickly computes summary statistics (mean, median, minimum, maximum, and count) on a numeric variable grouped by a categorical variable.

It also produces a ggplot object- boxplot which visually presents some of the summary statistics found in the summary table generated such as median, minimum, maximum, and count.

Below is a basic example which shows you how to use the function:

```{r example}
library(statsummary)
summarize_data(gapminder::gapminder, continent, lifeExp)
```

